\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-17 manuscript/manuscript.tex
sp100

From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
although the extent to which the p-values appear to be 
completely aligned with the line
in the Q-Q plots is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in the Q-Q plots, even
in Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high. Additionally, performance generally seems
better for negative $\tau$ values versus positive $\tau$ values of the same
strength.

@@

From 
Table~\ref{fig:rr}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is slightly higher for the $\Gamma(8, 1)$ sample 
than for 
the $N(8, 8)$. As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.

>>>>

From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
although the extent to which the p-values appear to be 
completely aligned with the line
in the Q-Q plots is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in the Q-Q plots, even
in Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high. Additionally, performance generally seems
better for negative $\tau$ values versus positive $\tau$ values of the same
strength. Results are very similar for normal and gamma margins.

@@

From 
Figure~\ref{fig:rr}, 
the rejection rates appear to get lower as $\tau$ increases in a
positive direction. Using a sample size $n \geq 800$ appears to be sufficient
when $\tau$ is not too high, but for $\tau \geq 0.75$, all sample sizes 
observed appeared to have less than desirable rejection rates. Results
do not appear to be to different when comparing gamma and normal 
margins, indicating that the method is robust to the marginal distribution.
